%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Freelance} % Organization
    {Remote} % Location
    {Jun. 2010 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Native android apps from scratch}. 
        \item {Code maintaining, debugging, profiling and rework focused on performance and user experience. Integration of several third party libraries. Development of new functionalities and requirements based on the new Android APIs.}
        \item {Rewriting and code maintenance of desktop and mobile high traffic sites.}
        \item {Migration and initial setup of development environment for aws stack using docker, vagrant and chef.}
        \item {Implementation of many external providers and creation of multiple APIs for high traffic consumers using several server-side authentication and caching strategies.}
        \item {Implementation of metrics, structured-data and SEO-friendly version of sites.}
        \item {Query optimization (db, solr, elasticsearch)}.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {3d | Motion Graphics} % Job title
    {VDNMedia} % Organization
    {Ciudad de Buenos Aires, Argentina} % Location
    {Dic. 2008 - Dic. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modeling, texturing, lighting and 3D animation with Autodesk Maya and Blender.}
        \item {Facial and body animation with Autodesk MotionBuilder.}
        \item {2D and 3D animation creation from integrated work on Photoshop and After Effects.}
        \item {Interactive games development on Flash (as 2.0 and as 3.0).}
        \item {3D micro-show design for kids.}
        \item {TV shows aestethics creation.}
        \item {Video post-production.}
        \item {Audio editing.}
        \item {Multiformat and multipurpose video editing.}
        \item {Desktop Publishing.}
        \item {Interactive game development for Tv shows (also including hardware and software technical support).}
        \item {Design and development of agency website.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Video post production / video editor} % Job title
    {Woler Pro\&Post} % Organization
    {Ciudad de Buenos Aires, Argentina} % Location
    {Jan. 2006 - Dic. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lineal and non-linear video editing on multiple formats through hardware controllers and Final Cut Studio.}
        \item {3D modeling with Autodesk Maya 2008.}
        \item {2D and 3D animation creation from integrated work on Photoshop and After Effects.}
        \item {Aestethics and motion graphics for TV shows, internal or corporate videos on several formats.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
